Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-06 analysis/paper/paper.qmd
Figures 1 and 4

@@

>>>>

![Overview of study area. Circles indicate the locations of the US Antarctic Marine Living Resources (AMLR) station grid. Solid and dashed gray lines represent the 1000 and 2500 m isobaths, respectively. Not all stations were sampled every year. Inset indicates the location of the study area (red shading) relative to South America and the Antarctic Peninsula (BS: Bellingshausen Sea; WS: Weddell Sea). Bathymetry from IBCSO v2 [@dorschelInternationalBathymetricChart2022]; land from Natural Earth (www.naturalearthdata.com).](images/fig-overviewmap.png){#fig-overviewmap width="116mm"}

@@

```{r}
#| label: fig-predclustannual
#| fig-cap: "Geographic distribution of predator communities in each survey year (A–E: 2012–2016, respectively). Areas of extensive sea-ice coverage are indicated by blue gradient, where satellite-derived mean sea-ice coverage in the month of August in each year exceeded 65%."
#| out-width: 169mm
#| out-height: 121mm

make_fig_predclustannual(
  read_obj("stations_clust"), 
  read_obj("seaice_conc_df")
)
